Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
abstract

\begin{abstract}
  We formalize and investigate two approaches to designing convex surrogate loss functions for problems such as classification or ranking.
  First, one can attempt to ``embed'' each prediction (label, ranking, etc) as a point in $\reals^d$ and design a convex loss function on that space.
  Second, one can use a piecewise-linear convex, or polyhedral loss.
  We prove that these approaches are equivalent in power, giving several characterizations of each, and show that every loss with a finite number of possible labels has a surrogate of both forms.
  Then, we investigate the dimensionality of the surrogate hypothesis space.
  We give a complete characterization of the $1$-d case.
  In higher dimensions, we give necessary conditions and a novel lower bound for abstain loss.
\end{abstract}

@@

\paragraph{Other necessary conditions.}
One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}

Another is a reduction to the one-dimensional characterization. If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
At this point, the one-dimensional characterization may rule out embeddability.

>>>>

\begin{abstract}
  We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and convexifying the loss.
  We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the $1$-d case, and several necessary conditions in higher dimensions.
  We illustrate our results with new lower bounds for abstain loss.
\end{abstract}

@@

\paragraph{Other necessary conditions.}
One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
Another is a reduction to the one-dimensional characterization. If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
At this point, the one-dimensional characterization may rule out embeddability.
